A Switching Planner for Combined Task and Observation Planning

### 2011-02-03 code/subarchitectures/planner.sa/trunk/src/latex/AAAI11/relatex.tex
New bibliography, and the related work section is begenning

@@

Our work is motivated by domains that contain a mixture of task
planning and observation planning. There have been a number of recent
papers representing observation planning problems as POMDPs and using
various techniques to manage the large state
space. \citeauthor{hippo-jnl}~(\citeyear{hippo-jnl}) take this
approach in a vision algorithm selection problem. In their case there
is a natural hierarchical decomposition of the problem which allows
them to solve large problems by breaking them into a set of small
POMDPs. \citeauthor{doshi08:pref_elic}~(\citeyear{doshi08:pref_elic})
represent a preference elicitation problem as a POMDP and take
advantage of symmetry in the belief space ---essentially the idea that
it does not matter what the value of the variable you are trying to
observe is--- to exponentially shrink the state space. Although we
have been actively exploring the \citeauthor{doshi08:pref_elic}
approach, we have yet to find those exploitable structures in our
domain due to the task planning requirement.

>>>>

\cite{wyattetal2010tamd}

For the purpose of symbolic
planning,~\cite{wyattetal2010tamd,talamadupula:2010,Kraft2008} treat
sensing deterministically and beliefs qualitatively.
%%
 Addressing specifically this second
challenge,~\citeauthor{talamadupula:2010} identify
\emph{continual planning} in the presence of detailed probabilistic
 models as an important direction for future research.

Focusing now specifically on planning, our work is motivated by
domains that contain a mixture of task planning and observation
planning. There have been a number of recent papers representing
observation planning problems as POMDPs and using various techniques
to manage the large state
space. \citeauthor{hippo-jnl}~(\citeyear{hippo-jnl}) take this
approach in a vision algorithm selection problem. In their case there
is a natural hierarchical decomposition of the problem which allows
them to solve large problems by breaking them into a set of small
POMDPs. \citeauthor{doshi08:pref_elic}~(\citeyear{doshi08:pref_elic})
represent a preference elicitation problem as a POMDP and take
advantage of symmetry in the belief space ---essentially the idea that
it does not matter what the value of the variable you are trying to
observe is--- to exponentially shrink the state space. Although we
have been actively exploring the \citeauthor{doshi08:pref_elic}
approach, those exploitable structures are not present in our domain
due to the task planning requirement.

\cite{shani:etal:08}

Generally There has been much recent work on scaling POMDP solution procedures
to medium-sized instances. In the case of general domain-independent
factored systems, the state-of-the-art scales to relatively small
problems with $2^{22}$
states~\cite{shani:etal:2008}.\footnote{Considering only room
categories and distribution of objects, problems we consider in this
paper have $\sim 10^{27}$ states. The details of view points, from
local active visual search, and those of robot location, further
increase that figure. Therefore, not only because they are offline,
but also because they have limited scalability, these approaches are
infeasible in our setting.} At their limit, these procedures take over an
hour to converge.  For classes of POMDP that feature exploitable
structures (e.g., no actions with negative effects), problems with as
many as $10^{30}$ states can be targeted by offline
procedures~\cite{brunskill:russell:2010}. Moving someway towards
addressing all the challenges we have outlined, recent online POMDP
solution procedures have been developed which can exploit highly
approximate value functions -- typically computed using a point-based
procedure -- and heuristic in forward
search~\cite{ross:etal:2008}. Their applicability in our setting is
limited due to the large amount of
\emph{problem-specific} offline processing required to get useful
search guidance. A {\em very} recent and promising online approach for
large POMDPs employs Monte-Carlo sampling to break the curse of
dimensionality in situations where goal reachability is
easy~\cite{silver:veness:2010}. Although we suppose it an interesting
item for future work to pursue that direction, it should be noted that
ease of goal reachability is not guaranteed in the problems we face,
and is certainly not a property to be assumed in domain independent
planning.

@@
